--- 
title: "Schweppe Lab Handbook"
author: "Devin Schweppe"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is a lab handbook for the Schweppe Lab within the Department of Genome Sciences at the University of Washington."
---

# Welcome!

Welcome to the Schweppe Lab Handbook.The handbook was developed by the [Devin Schweppe](https://schweppelab.org/) as a guide for new and current members of the lab. The goal of this handbook is to provide resources, guidelines, and information to foster an environment of scientific excellence and personal development that is inclusive and (hopefully) fun. More information on the lab and department can be found through the following resources:

*The Lab website: (https://schweppelab.org)
*The Lab Slack Channel: (https://schweppelab.slack.com/)
*Departmental website: (https://www.gs.washington.edu/)


The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
